### 2015-06-30 narrative/data-desc.tex

One of the key advantages for a storage system to communicate through objects rather than 
bytes is that it gives a meaning and relationship of certain bytes placed together to form one object.
This permits the system to understand that all of the data in an object needs to be organized together,
and that commonly the entire object will be written and read. Data Models then constitute a collection
of objects which are then placed together via a relationship. In other words, we can think of a
simulation which contains a three dimensional mesh, and that the coordinates of the mesh, along
with the connectivity of the mesh will generally be accessed together. This also us to organize
the data in the storage system in such a way that will allow a user to easily to describe this 
collection of data together, and it will allow the user to describe relationships between the objects
in the data model.

>>>>

One of the key advantages of representing data as \textit{objects}, rather than 
bytes, is that it allows data semantics, user intentions, QoS requirements, and
the relationship between user data to be readily captured and embedded with the 
raw data. This description of data, as enabled by managing data as objects, bridges 
the semantics gap between applictions, middleware, and storage systems,
and allows the system to understand user-level data, execute QoS requirements, and
optimize application or system performance.

Data Models then constitute a collection
of objects which are then placed together via a relationship. In other words, we can think of a
simulation which contains a three dimensional mesh, and that the coordinates of the mesh, along
with the connectivity of the mesh will generally be accessed together. This also us to organize
the data in the storage system in such a way that will allow a user to easily to describe this 
collection of data together, and it will allow the user to describe relationships between the objects
in the data model.

### 2015-06-30 narrative/intro.tex

\subsection{Storage System Perspective}
\label{subsec:storage-perspective}
From the perspective of the storage system, it is necessary to manage the data from
a given user request amongst all of the requests from all users, and try to optimize the
entire system accordingly. Today the problem is that when a user writes there is a
tremendous amount of interference from other users on the system who may be
writing or reading at the same time. By requiring a certain quality
of service the system must potentially lock out users with lower currency
they want to place in the reading or writing of their data. The storage
system must also automatically move data from one tier of the storage to
another, without effecting the quality of service that it guarantees at the
time of questioning. The storage system must also look at ways to organize
data amongst all of the tiers of storage in one consistent way.

One of the clear research objectives of this project is to understand how the
storage system can interact with the middleware (application-aware) piece so
that the data with the highest utility is kept on the fastest layers of the
storage system for as long as specified. Clearly we need to maintain 
QoS such that fuzzy-estimates of the time it will take to write/read data from
the different layers informs any migration/eviction decisions, and clearly it
is critical that the storage system can manage the data across all of the
layers. We will use learning techniques to automatically migrate data
sub-objects across the hierarchy as well as to eventually evict data which is
large and has very low utility.

>>>>

\subsection{Storage System Perspective}
\label{subsec:storage-perspective}
From the perspective of the storage system, it is necessary to manage the data from
a given user request amongst all of the requests from all users, and try to optimize the
entire system accordingly. Today the problem is that when a user writes there is a
tremendous amount of interference from other users on the system who may be
writing or reading at the same time. By requiring a certain quality
of service the system must potentially lock out users with lower currency
they want to place in the reading or writing of their data. The storage
system must also automatically move data from one tier of the storage to
another, without affecting the quality of service that was offered at request
time. The storage system must be able to organize
data amongst all of the tiers of storage in a known, consistent way.

One of the clear research objectives of this project is to understand how the
storage system can interact with the middleware (application-aware) piece so
that the data with the highest utility is kept on the fastest layers of the
storage system for as long as specified. Clearly we need to maintain 
QoS such that fuzzy estimates of the time it will take to write/read data from
the different layers informs any migration/eviction decisions, and clearly it
is critical that the storage system can manage the data across all of the
layers. We will use learning techniques to automatically migrate data
sub-objects across the hierarchy as well as to eventually evict data which is
large and has very low utility.
